---
title: "R if_else"
author: "Chang"
date: "2021/9/30"
output: html_document
---

### review

#### practice 1: Generate 50 standard normal numbers and remove observations whose values are greater than 2. Save the result to be a new vector

```{r}
n = 50
x <- rnorm(n, 0, 1) # normal distribution
temp <-  x < 2 # temp:暫時的，右方設定判斷句(留下x < 2的)
y <- x[temp] # 留下指定的x值
head(y)
```

#### practice 2: Generate 50 standard normal numbers and keep observations whose values are greater than the sample mean±2*S.D.
```{r}
set.seed(1)
n = 50
x <- rnorm(n, 0, 1)
xbar <- mean(x)
std <- sd(x)
temp <-  x > xbar+2*std | x < xbar-2*std
y <- x[temp]
y
```

### rep(重複的東西, 重複次數)
```{r}
rep(1:4, 2)
z <- rep(NA, n)
head(z)
```

### NULL:不清楚資料長度時使用，逐次加入合併
```{r}
t <-  NULL # 空集合
t <-  c(z, t) # t被z佔據
t

# t與50個binomial亂數合併
t <- c(t, rbinom(n, 0, 0.5)) 
t
length(t)
```


### matrix(元素值, #rows, #columns)

### array(元素值, 維度)
```{r}
m <- matrix(NA, 2, 5)
m
w <- array(NA, dim = c(2, 5, 2))
w
# exercise 1:
# by matrix()
w0 <- matrix(1:10, 2,5 , byrow = T)
w0
# by array()
w1 <- array(1:10, dim = c(5,2))
t(w1)

# 分號的功能相當於換行
x <- 0.5
y <- 0    # x <- 0.5; y <- 0
```

### 條件句: if_else
```{r}
if (x > 3){
  y <- 1
} else{
  y <- 2
}
y
### use ifelse to do the same thing
ifelse(x > 3, 1, 2)
```

#### Practice 3
```{r}
# absolute value
x <- -3
# y <- 0  一開始可以不用指定新變數
if (x >= 0){
    y <- x
} else{
    y <- abs(x)
}
y

# evaluate f(5)
x <- 5
# y <- 0
if (x < 0){
    y <- 0
} else{
    y <- x
}
y 

# find f(x) for x is a uniform number in (-2, 2)
#set.seed(2)
x <- runif(1, min = -2, max = 2)
if (x < 0){
  0 
} else{
  x 
}

#小學生 數學&閱讀成績
#透過sample()找60~100取數學分數，80~100取閱讀分數
#條件:數學成績 >= 90 且 閱讀成績 >= 95，回傳good，否則keep going
math <- sample(60:100, 1)
reading <- sample(80:100, 1)
if (math >= 90 & reading >= 95){
    score <- c(math, reading)
    print("good")
} else{
    score <- c(math, reading)
    print("keep going")  
}
score
```

#### 條件有先後順序:先看閱讀再看數學
```{r}
# 把原數值加碼儲存在原變數
math <- sample(60:100, 1)
reading <- sample(80:100, 1)
if (reading >= 95){
    score <- c(math, reading)
    result = 80
}
if (math >= 95){
    score <- c(math, reading)
    result = result + 20
} else {
    score <- c(math, reading)
    result = 60
}
score
result
```

### 兩個以上條件句
```{r}
x <- runif(1, -5, 5)
if (x < 0){
    y <- 0
} else if (x < 1 & x >= 0){
    y <- x
} else{
    y <- 1
}
y

#小學生 數學&閱讀成績
#透過sample()找60~100取數學分數，80~100取閱讀分數
#條件:如果數學 >= 90 且閱讀 >= 95，回傳100，只有閱讀 >= 95，回傳80，其他回傳60
math <- sample(60:100, 1)
reading <- sample(80:100, 1)
if (math >= 90 & reading >= 95){
  score <- c(math, reading)
  print("100")
} else if (reading >= 95){
  score <- c(math, reading)
  print("80") 
} else {
  score <- c(math, reading)
  print("60")
}
score

```




