---
title: "1014_review_and_exercise"
author: "Chang"
date: "2021/10/15"
output: 
  html_document:
    toc: true
    toc_float: true
---
 * cat() and print()

 * review:
 
 1. names(x) <- c("a", "b", ...) 命名
 
 2. return 後面的工作會被ignore
 
 3. return 

### exercise A
```{r}
f.fun <- function(x, c){
  if (x < -1){
    -c
  } else if (-1 <= x  | x <= 1){
    x
  } else{
    c
  }
}
c(f.fun(-5,1), f.fun(1, 1), f.fun(5, 1))
c(f.fun(-5, 10), f.fun(1, 10), f.fun(5, 10))
```
### exercise B
Write a function in R to get a size n of data set follows a multivariate normal distribution with mean (0, 0) and covariance matrix is (1,ro,ro,1)

 * the input is (n,ro)
 
 * the output is a data matrix with dim= n by 2
 
 * In addition, report the sample correlation, sample means and sample variances for each variable
```{r}
n <-  10
ro <-  0.5
covm <- matrix(c(1, ro, ro, 1), nrow = 2, ncol = 2)
result <- mvtnorm::rmvnorm(n, mean = c(0,0), sigma = covm)
colnames(result) <- c("x", "y")
result <- as.data.frame(result)
result
cor(result$x,result$y)
mean(result$x)
mean(result$y)
var(result$x)
var(result$y)
```


### exercise C
```{r}
# (a)
m <- 1:20
x <- m[seq(1, 20, 2)]
y <- m[-seq(1, 20, 2)]
f <- function(x, y){
  z <- x + y
  return(prod(z))
}
f(x,y)

# (b)
f1 <- function(x, y){
   sum(x / y)
  }
f1(x,y)

# (c)
f2 <- function(x, y){
    sum(x^3*y^2)
}
f2(x,y)
```

### exercise D
```{r}
# (a)
n <- 100
k <- seq(1:n)
x <- k[seq(1, n, 2)]
y <- k[-seq(1, n, 2)]
f.fun <- function(x, y){
  z <- x + y
  return(prod(z))
}
f.fun(x,y)

# (b)
f.fun1 <- function(x, y){
  sum(x / y)
}
f.fun1(x,y) 

# (c)
f.fun2 <- function(x, y){
  sum(x^3*y^2)
}
f.fun2(x,y)
```


### exercise E
```{r}
score <- sample(1:100, 50, T)
my.test <- function(score){
  if (length(score[score >= 60]) > 25 & length(score[score > 90]) >= 1){
    print(
      paste("本次成績不調分，平均分數為", mean(score), sep = "")
      )
  } else{
    print(
      paste("本次成績會調分，不及格比例為", round(length(score[score < 60])/50, 2)*100, "%", sep = "")
      )
  }
}
my.test(score)
```
